# Debugging

## "printf" tracing
```{r eval = FALSE}
cat(file=stderr(), "drawing histogram with", 1, "bins\n")
```

## Unconditional breakpoints
Just click next to a line in Rstudio.

## Conditional breakpoint
```{r eval=FALSE}
if (input$bins > 50)
  browser()
```

## Showcase Mode
```{r eval=FALSE}
runApp(..., display.mode="showcase")
```

## Reactive Log
```{r eval=FALSE}
options(shiny.reactlog=TRUE)
runApp(...)
showReactLog()
```

## Client/server tracing
```{r eval = FALSE}
options(shiny.trace = TRUE)
```

SEND {"config":{"workerId":"","sessionId":"04531d50d12554bd981b24b9d3983cc4"}}
RECV {"method":"init","data":{"bins":30,".clientdata_output_distPlot_width":610,
  ".clientdata_output_distPlot_height":400,".clientdata_output_distPlot_hidden":false,
  ".clientdata_pixelratio":1,".clientdata_url_protocol":"http:",
  ".clientdata_url_hostname":"127.0.0.1",".clientdata_url_port":"5569",
  ".clientdata_url_pathname":"/",".clientdata_url_search":"",
  ".clientdata_url_hash_initial":"",".clientdata_singletons":"",
  ".clientdata_allowDataUriScheme":true}}

# Error Handling
## Tracebacks

```{r eval=FALSE}
if (input$bins > 40)
  stop("too many bins")
```

## Full tracebacks
```{r eval=FALSE}
options(shiny.fullstacktrace = TRUE)
```

## Pausing on errors
```{r eval = FALSE}
options(shiny.error = browser)
```